\thetitle

### 2020-07-24 writing/introduction.tex
adding to the intro academic claim about useless blame

The divisions in the academic and industrial world of gradual typing raise the question 
\begin{quote}
 \it
 whether blame assignment adds any value to a gradually typed language, \\
 especially for the benefit of the working programmer.
\end{quote}
Given the prominence of blame in academia and its complete absence in
industrial systems, it comes as an even bigger surprise that the research
literature and the industrial blog world do not present or discuss any
possible answers.  Instead, when language designers decide to look into the
question, they seem to answer it one way or another without any scientific
justification. As a matter of fact, the research community simply does not have a
method for evaluating blame, and given the question's practical
relevance, this a significant problem.

>>>>

The divisions in the academic and industrial world of gradual typing raise the question 
\begin{quote}
 \it
 whether blame assignment adds any value to a gradually typed language, \\
 especially for the benefit of the working programmer.
\end{quote}
Given the long standing academic interest in blame  and its complete absence in
industrial systems, it comes as an even bigger surprise that the research
literature and the industrial blog world do not present or discuss any
possible answers.  Instead, when language designers decide to look into the
question, they seem to answer it one way or another without any scientific
justification. As a matter of fact, the research community simply does not have a
method for evaluating blame, and given the question's practical
relevance, this a significant problem.
